Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-06-05 manuscript.tex
applying comment

\documentclass[lettersize,journal]{IEEEtran}

@@

% ------------------------------------
% Robot Model Figure and Table
% ------------------------------------
\begin{figure}[t]
    \centering
    \subfloat[Two-link robotic manipulator.\MSRY{ADD inertia}]{
        \includegraphics[width=0.65\linewidth]{src/figures/RobotModel.drawio.pdf}
        \label{fig:robot:model}
    }
    \hfill
    \subfloat[Control input saturation function.]{
        \includegraphics[width=0.55\linewidth]{src/figures/saturation.drawio.pdf}
        \label{fig:robot:sat}
    }
    \caption{Two-link robotic manipulator and control saturation function.}
    \label{fig:robot}
\end{figure}

@@

The tracking performances of CONAC with control input constraints, \ie (C$_1$), and (C$_2$), outperformed CONAC with the auxiliary system (C$_4$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
This is because, (as will be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
The tracking performance of (C$_3$) was also better than (C$_4$), but this is because (C$_3$) utilized more capability of the actuator than (C$_4$) without considering the control input saturation.
One may conclude that (C$_3$) outperformed (C$_4$) since the tracking performance of (C$_3$) was better than (C$_4$), as shown in Table~\ref{tab:sim:L2}.
However, since the CONAC adapts the weights to reduce the tracking error, \ie which is the only feedback signal, the CONAC increases the control input excessively large to reduce the tracking error, which can not be regulated due to the actuator limits.
In Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, the violations of the control input saturations grow larger in every saturated time interval.
Moreover, this large violation occurs oscillations when the control saturation is released as the reference trajectory is changed, since the weights are adapted to produce large control inputs.

% ------------------------------------
% Control Input Saturation
% ------------------------------------
\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ in time interval from $29.4$ s to $31.9$ s (bird's eye view).]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $29.4$ s to $31.9$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $29.4$ s to $31.9$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, and (C$_4$) \protect\colorLine{magenta}{solid} in time interval from $29.4$ s to $31.9$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.6\linewidth]{
		src/figures/lambda_effect.drawio.pdf
		}
	\caption{
		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_2$.
		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively, i.e., $\lambda_{j}' > \lambda_{j}''$.
	}
	% \vspace{1mm}
	\label{fig:lambda_effect}
\end{figure}

@@

In this section, the constraint handling capability of all controllers are investigated.
As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}.
For (C$_1$) and (C$_2$), the control input saturation was handled using the Lagrange multipliers and, for (C$_4$), the auxiliary system was used to handle the control input saturation.
It is worth to note that the control input constraints were violated repeatedly after constraint handling, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.

Even though all controllers except (C$_3$) satisfied the input saturation, (C$_4$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $29.4$ s to $31.9$ s.
This is because, as aforementioned, the auxiliary system only considers saturation of each control input, and the maximum value of the first link's torque $\overline{\tau}_1$ was set to approximately match the maximum allowable norm of the control input $\overline\tau$.
In contrast, (C$_1$), and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$, defined in \eqref{eq:sat}, \ie see, Fig.~\ref{fig:robot:sat}.

@@

% zeta
The detail of the constraint handling in the time interval from $29.4$ s to $31.9$ s, is now investigated.
First, for (C$_4$), the auxiliary state $\zeta_1$ was generated by control input saturation of the first link actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:aux}.
As the weights were adapted to reduce not only the filtered error $\fe$ but also the auxiliary state $\mv{\zeta}$, the control input saturation was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
After the saturation was resolved, the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as described in Fig.~\ref{fig:ctrl:result:scope:aux}.

% beta + zeta
For the cases of (C$_1$) and (C$_2$), the Lagrange multipliers $\lambda_j\in\forall j\in\mathcal{I}$ adjusted the adaptation direction of the weights $\estwth_i,\ \forall i\in\{0,1,2\}$ to reduce the constraint violation $c_j\in\forall j\in\mathcal{I}$, as $\lambda_j\in\forall j\in\mathcal{I}$ generated by the constraint violations.
% comparison; big, small beta
The effect of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$ on the adaptation direction of the weights $\estwth_2$ is shown in Fig.~\ref{fig:lambda_effect} for a constraint $c_j,\ \forall j\in\mathcal{I}$, with two different amplitudes.
It is noteworthy that the constraint $c_j$ which satisfies Assumptions \ref{assum:convex} and \ref{assum:LICQ}, is convex in $\estwth_2$-space, \ie see, Lemma. \ref{lem:convex:angle}.
The bigger and smaller Lagrange multipliers can be interpreted as the case of (C$_1$) and (C$_2$), respectively, since the update rates of the Lagrange multipliers were set to $10^2$ times bigger for (C$_1$) than (C$_2$).
This results in a fast growth of the Lagrange multipliers $\lambda_j$, when the constraint was violated, \ie see, \eqref{eq:adap:lbd}.
With the bigger $\lambda_j'$, the adaptation of $\estwth_2$ is more assertive than that with smaller $\lambda_j''$.
This leads to a faster satisfaction of the constraint $c_j$, but this also causes oscillation in the adaptation process.

Hence, invoking above discussion, the real-time implementation results of (C$_1$) and (C$_2$) are compared in Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}.
In the figures, $\lambda_{\rbu}$ of (C$_1$) repeatedly increased and disappeared, which indicates that the constraint $c_{\rbu}$ was violated and satisfied, respectively, in the discrete time implementation.
Besides, with small $\lambda_{\rbu}$, the adaptation direction of $\estwth_2$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_{\rbu}$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
This allows the controller to show a smoother control input.

@@

\KHCH{반복해서 이 내용을 설명할 필요가 있을까요?}
\MSRY{가중치 제약조건 만족에 대한 이야기가 없어서 추가했습니다.}
The details of the constraint handling process are shown in Fig.~\ref{fig:ctrl:result:scope}, as well.
In Fig.~\ref{fig:ctrl:result:scope:beta}, the Lagrange multipliers $\lambda_{\theta_2}$ were increased by the weight $\estwth_2$ exceeds the weight norm constraint $\overline\wth_2$, and the adaptation direction of the weights $\estwth_2$ was adjusted to resolve the violation of the constraint $c_{\theta_2}$.

@@

Since the proposed CONAC was implemented in discrete time, demonstration regarding the KKT conditions in steady state is not straightforward.
However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of the active constraints were positive and inactive constraints were zero.

@@

The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time using CPU clock ticks of the OpenCR1.0 board.
The computational times shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}, indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz.

>>>>

\documentclass[journal]{IEEEtran}

@@

% ------------------------------------
% Robot Model Figure and Table
% ------------------------------------
\begin{figure}[t]
    \centering
    \subfloat[Two-link robotic manipulator.]{
        \includegraphics[width=0.65\linewidth]{src/figures/RobotModel.drawio.pdf}
        \label{fig:robot:model}
    }
    \hfill
    \subfloat[Control input saturation function.]{
        \includegraphics[width=0.55\linewidth]{src/figures/saturation.drawio.pdf}
        \label{fig:robot:sat}
    }
    \caption{Two-link robotic manipulator and control saturation function.}
    \label{fig:robot}
\end{figure}

@@

The tracking performances of CONAC with control input constraints, \ie (C$_1$), and (C$_2$), outperformed CONAC with the auxiliary system (C$_4$) in the second episodes, as shown in Table~\ref{tab:sim:L2}.
This is because, (as will be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
The tracking performance of (C$_3$) was also better than (C$_4$), but this is because (C$_3$) utilized more capability of the actuator than (C$_4$) without considering the control input saturation.
\KHCH{
        여기부터 문단 끝날때까지의 표현이 명료하지 않습니다. C3의 tracking performance가 좋은 것은 지표상으로 명확히 맞는 말이기 때문에 마치 tracking performance가 실제로 좋은 것은 아니다라는 뉘앙스의 논리 전개가 적절치 않습니다.

    Tracking performanc는 더 좋지만 과도한 control input을 사용하고, saturation이 지난 이후에는 진동 문제가 있다는 것만 명료하게 표현해주세요.
}
One may conclude that (C$_3$) outperformed (C$_4$) since the tracking performance of (C$_3$) was better than (C$_4$), as shown in Table~\ref{tab:sim:L2}.
\KHCH{어색한 표현; 수정 요}\MSRY{필요없는 내용으로 판단하여 삭제했습니다.}
However, during the episodes, (C$_3$) increases the control input excessively large to reduce the tracking error, even though it can not be regulated due to the actuator limits as shown in Fig.~\ref{fig:ctrl:result:tau:2} and Fig.~\ref{fig:ctrl:result:tau:norm}, \ie the violations of the control input saturations of (C$_3$) grow larger in every saturated time interval.
Moreover, this large violation occurs oscillations when the control saturation is released as the reference trajectory is changed, since the weights are adapted to produce large control inputs.

% ------------------------------------
% Control Input Saturation
% ------------------------------------
\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ locus in time interval from $29.4$ s to $31.9$ s.]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $29.4$ s to $31.9$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $29.4$ s to $31.9$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, and (C$_4$) \protect\colorLine{magenta}{solid} in time interval from $29.4$ s to $31.9$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.6\linewidth]{
		src/figures/lambda_effect.drawio.pdf
		}
	\caption{
		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_2$.
		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of large and small Lagrange multiplier, respectively, i.e., $\lambda_{j}' > \lambda_{j}''$.
	}
	% \vspace{1mm}
	\label{fig:lambda_effect}
\end{figure}

@@

In this section, the constraint handling capability of all controllers are investigated.
As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}.
For (C$_1$) and (C$_2$), the control input saturation was handled using the Lagrange multipliers and, for (C$_4$), the auxiliary system was used to handle the control input saturation.

Even though all controllers except (C$_3$) satisfied the input saturation, (C$_4$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $29.4$ s to $31.9$ s.
This is because, as aforementioned, the auxiliary system only considers saturation of each control input, and the maximum value of the first link's torque $\overline{\tau}_1$ was set to approximately match the maximum allowable norm of the control input $\overline\tau$.
In contrast, (C$_1$) and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$, defined in \eqref{eq:sat}, \ie see, Fig.~\ref{fig:robot:sat}.

@@

% zeta
The detail of the constraint handling in the time interval from $29.4$ s to $31.9$ s, is now investigated.
First, for (C$_4$), the auxiliary state $\zeta_1$ was generated by control input saturation of the first link actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:aux}.
As the weights were adapted to reduce not only the filtered error $\fe$ but also the auxiliary state $\mv{\zeta}$, the control input saturation was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
After the saturation was resolved at 31 seconds (see Fig.~\ref{fig:ctrl:result:tau:norm}), the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as described in Fig.~\ref{fig:ctrl:result:scope:aux}.

% beta + zeta
For the cases of (C$_1$) and (C$_2$), the Lagrange multipliers $\lambda_j\in\forall j\in\mathcal{I}$ adjusted the adaptation direction of the weights $\estwth_i,\ \forall i\in\{0,1,2\}$ to reduce the constraint violation $c_j\in\forall j\in\mathcal{I}$, as $\lambda_j\in\forall j\in\mathcal{I}$ generated by the constraint violations.
% comparison; big, small beta
The effect of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$ on the adaptation direction of the weights $\estwth_2$ is shown in Fig.~\ref{fig:lambda_effect} for a constraint $c_j,\ \forall j\in\mathcal{I}$, with two different amplitudes.
It is noteworthy that the constraint $c_j$ which satisfies Assumptions \ref{assum:convex} and \ref{assum:LICQ}, is convex in $\estwth_2$-space (see Lemma. \ref{lem:convex:angle}).
The large and small Lagrange multipliers can be interpreted as the case of (C$_1$) and (C$_2$), respectively, since the update rates of the Lagrange multipliers were set to $10^2$ times larger for (C$_1$) than (C$_2$).
This results in a fast growth of the Lagrange multipliers $\lambda_j$, when the constraint was violated, \ie see, \eqref{eq:adap:lbd}.
With the larger $\lambda_j'$, the adaptation of $\estwth_2$ is more assertive than that with smaller $\lambda_j''$.
This leads to a faster satisfaction of the constraint $c_j$, but this also causes oscillation in the adaptation process.

Hence, invoking above discussion, the real-time implementation results of (C$_1$) and (C$_2$) are compared in Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}.
In the figures, $\lambda_{\rbu}$ of (C$_1$) repeatedly increased and disappeared, which indicates that the constraint $c_{\rbu}$ was violated and satisfied, respectively, in the discrete time implementation.
Besides, with small $\lambda_{\rbu}$, the adaptation direction of $\estwth_2$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and  positive Lagrange multiplier $\lambda_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}.
This allows (C$_2$) to show a smoother control input.

@@

The details of the constraint handling process are shown in Fig.~\ref{fig:ctrl:result:scope}, as well.
In Fig.~\ref{fig:ctrl:result:scope:beta}, the Lagrange multipliers $\lambda_{\theta_2}$ were increased by the weight $\estwth_2$ exceeds the weight norm constraint $\overline\wth_2$, and the adaptation direction of the weights $\estwth_2$ was adjusted to resolve the violation of the constraint $c_{\theta_2}$.

\KHCH{
    이부분은 "worth to note"하지는 않아보입니다. 그리고 FIg 5에서 이 것을 확인하기도 어렵습니다. 굳이 이내용을 유지하려면 Fig 6에서 multiplier가 발생했다 사리지는 현상을 표현할 때 사용해주세요.
}
\MSRY{
    부드럽게 제약조건만족이 안되는 것에 대한 변명(?)으로 포함하고 싶었습니다. 
    그렇기에 제약조건 파트 제일 마직막으로 뺐습니다.
}
In addition, it is worth to note that the control input constraints were repeatedly violated even after the constraint handling, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
This is because the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.

@@

Since the proposed CONAC was implemented in discrete time, demonstration regarding the KKT conditions in steady state is not straightforward.
However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of the active constraints were positive and those of inactive constraints were zero.

@@

The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time using CPU clock ticks of the OpenCR1.0 board.
The computational times shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}, indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz, since the computational time of all controllers was less than $4$ ms.
